---
title: "Appendix"
author: "Kashaun Eghdam and Timothy Regis"
date: "10/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results='hide'}
# Loading in Required Packages
library(tidyverse)
```

```{r, results='hide'}
#This code chunk is what designs our main survey dataset
set.seed(314)
pop <- 11796032
survey_size <- 1000000
my_data2 <- tibble(
# Simulation for question "What is your age".
  Age = sample(x = 
                 c("18 to 24", "25 to 34", "35 to 44", 
                 "45 to 54", "55 to 64", "65 to 74",
                   "75+", "Prefer not to say")
               ,size = survey_size,replace = TRUE,
               prob = c(0.11, 0.152, 0.15, 0.18, 0.165,
                           0.11, 0.112, 0.02)),
# Simulation for question "How likely are you to vote in the upcoming election?".
  Likelyhood_Vote =sample(x = c("Very likely", "Likely",
                     "Unlikely", "Very Unlikely",
                     "Don't Know/Prefer Not to answer"),
               size = survey_size, replace = TRUE,
               prob = c(0.375, 0.375, 0.115, 0.115, 0.02)),

# Simulation for question "How satisfied are you with the current operation of the Ontario government?".
  Current_Gov =sample(x = c("Very satisfied", "Satisfied",
                     "Neither satisfied nor dissatisfied", 
                     "Dissatisfied", "Very dissatisfied"),
               size = survey_size, replace = TRUE,
               prob = c(0.01, 0.25, 0.05, 0.35, 0.25)),

# Simulation for question "What is your opinion on the Minimum Wage rate in the Province?".
  Min_Wage =sample(x = c("Too high", "Just right",
                     "Too low", "Don't care/NA"),
               size = survey_size, replace = TRUE,
               prob = c(0.20, 0.23, 0.54, 0.03)),

# Simulation for question "In your opinion, taxes for those with an income".
# Income less than $40,000.
  Taxes_low =sample(x = c("Should be Higher","Should Stay about the Same",
                     "Should be Lower", "Don't Care/NA"),
                     size = survey_size, replace = TRUE, 
                     prob = c(0.07, 0.24, 0.65, 0.04)),
# Income between $40,000 and $200,000.
  Taxes_mid =sample(x = c("Should be Higher", "Should Stay about the Same",
                     "Should be Lower", "Don't Care/NA"),
                     size = survey_size, replace = TRUE,
                     prob = c(0.08, 0.32, 0.55, 0.05)),
#Income greater than $200,000.
  Taxes_high = sample(x = c("Should be Higher", "Should Stay about the Same",
                     "Should be Lower", "Don't Care/NA"),
                     size = survey_size, replace = TRUE,
                     prob = c(0.67, 0.2, 0.08, 0.05)),

# Simulation for question "On a scale from 1 to 5, how important do you think the preservation of Ontario's environment is?".
  Environment =sample(x = c(1:5),
               size = survey_size, replace = TRUE,
               prob = c(0.1, 0.1, 0.1, 0.3, 0.4)),

# Simulation for question "How much money would you like to see go toward benefiting those on welfare?".
  Welfare =sample(x = c("Spend More", "Spend less",
                           "Spend about the same as previous year",
                            "Don’t know/No Opinion"),
               size = survey_size, replace = TRUE,
               prob = c(0.3, 0.25, 0.4, 0.05)),

#Simulation for question "How much money should be spent on Healthcare facilities in Ontario?".
  Healthcare =sample(x = c("Spend More", "Spend less",
                           "Spend about the same as previous year",
                            "Don’t know/No Opinion"),
                     size = survey_size, replace = TRUE,
                     prob = c(0.78, 0.10, 0.10, 0.02)),

# Simulation for question "What do you think about the current price of hydroelectricity in Ontario?". 
 Hydro =sample(x = c("Too expensive", "Too cheap",
                           "Fairly priced", "No Opinion"),
                     size = survey_size, replace = TRUE,
                     prob = c(0.75, 0.08, 0.15, 0.02)),

# Simulation for question "Through what avenue do you most judge a political candidate?". 
  Gather_info =sample(x = c("Candidate address and speeches", "Online news sources",
                        "TV", "Newspaper articles", "Social Media", "Other"),
                     size = survey_size, replace = TRUE,
                     prob = c(0.1, 0.25, 0.36, 0.5, 0.37, 0.03)),
)
```

```{r, fig.cap = 'Table 1', results='hide'}
set.seed(314)
my_data <- sample_n(my_data2, 10000)
head(my_data)
```

```{r,fig.cap = 'Figure 1' ,results='hide',warning=FALSE}
# Bar Graph for question "How satisfied are you with the current operation of the Ontario government?"
my_data %>%
  ggplot(aes(x = Current_Gov)) + 
  geom_bar(color = 'black', fill = 'Green') + 
  labs(title = "Voters' Satisfaction with Current Government", 
       x = "Level of Satisfaction", 
       y = "Number of Responses",
       caption = "Figure 1 - Source: Simulated dataset.") + 
  theme_minimal() + 
  geom_text(stat='count', aes(label=..count..), vjust=-1) + theme(axis.text.x=element_text(angle=45,hjust=1))
```

```{r, fig.cap="Figure 2",results='hide',warning=FALSE}
#Bar graph for question "What is your opinion on the Minimum Wage rate in the Province"
my_data %>%
  ggplot(aes(x = Min_Wage)) + 
  geom_bar(color = 'black',fill = "orange") + labs(title="Voter Opinions on the Current Level of Minimum Wage",
       x = "Opinion on current Minimum Wage",
       y = "Number of Responses",
       caption = "Figure 2 - Source: Simulated dataset.") +
  theme_minimal()
```

```{r, fig.cap="Figure 3.1",results='hide',warning=FALSE}
# Bar plot for question "In your opinion, taxes for those with an income:Less than $40,000"
my_data %>%
  ggplot(aes(x = Taxes_low)) + 
  geom_bar(color = 'black',fill = "orange") + 
  labs(title="Income Tax Rate Reccomendation for 
       Annual Income under $40,000 by Voters",
       x = "Reccomendation on Tax Rate",
       y = "Number of responses",
       caption = "Figure 3.1 - Source: Simulated dataset.") +
  theme_minimal()
```
```{r, fig.cap="Figure 3.2",results='hide',warning=FALSE}
#Bar plot for question "In your opinion, taxes for those with an income:Between $40,000 and $200,000"
my_data %>%
  ggplot(aes(x =Taxes_mid )) + 
  geom_bar(color = 'black',fill = "orange") +
  labs(title="Income Tax Rate Reccomendation for 
       Annual Income between $40,000 and $200,000 by Voters",
       x = "Reccomendation on Tax Rate",
       y = "Number of responses",
       caption = "Figure 3.2 - Source: Simulated dataset.") +
  theme_minimal()
```
```{r, fig.cap="Figure 3.3",results='hide',warning=FALSE}
# Bar plot for question"In your opinion, taxes for those with an income:Greater than $200,000"
my_data %>%
  ggplot(aes(x = Taxes_high )) + 
  geom_bar(color = 'black',fill = "orange") + 
  labs(title="Income Tax Rate Reccomendation for 
       Annual Income over $200,000 by Voters",
        x = "Reccomendation on Tax Rate",
        y = "Number of responses",
        caption = "Figure 3.3 - Source: Simulated dataset.") +
  theme_minimal()
```

```{r,fig.cap='Figure 4',results='hide', warning=FALSE}
#Bar plot for question "How much money should be spent on Healthcare in Ontario?"
my_data %>%
  ggplot(aes(x = Healthcare)) + 
  geom_bar(color = 'black',fill = "orange") +
  labs(title="Healthcare Spending Reccomendation by voters",
         x = "Spending Reccomendation", 
         y = "Number of responses",
         caption = "Figure 4 - Source: Simulated dataset.") + 
  theme_minimal()
```

```{r,fig.cap='Figure 5',results='hide',warning=FALSE}
# Bar plot for question "How much money would you like to see go toward benefiting those on welfare"
my_data %>%
  ggplot(aes(x = Welfare)) + 
  geom_bar(color = 'black',fill = "orange") + 
  labs(title="Welfare Spending Reccomendations by Voters",
       x = "Spending Reccomendation",
       y = "Number of responses",
       caption = "Figure 5 - Source: Simulated dataset.") +
  theme_minimal()
```

```{r,fig.cap='Figure 6',results='hide',warning=FALSE}
# Bar plot for question "On a scale from 1 to 5, how important do you think the preservation of Ontario's environment is?"
my_data %>%
  ggplot(aes(x = Environment)) + 
  geom_bar(color = 'black',fill = "orange") + 
  labs(title="Importantance of Protecting the Environment to Voters",
       x = "Level of Importance",
       y = "Number of responses",
       caption = "1 = Not Important, 5 = Very Important.                 Figure 6 - Source: Simulated dataset.") +
  theme_minimal()
```

```{r,fig.cap='Figure 7',results='hide',warning=FALSE}
# Bar plot for the question "What do you think about the current cost of hydroelectricity?"
my_data %>%
  ggplot(aes(x = Hydro)) + 
  geom_bar(color = 'black',fill = "orange") + 
  labs(title="Opinions on current Hydroelectricity Prices in Ontario",
       x = "Opinion",
       y = "Number of responses",
       caption = "Figure 7 - Source: Simulated dataset.") +
  theme_minimal()
```

```{r, fig.cap='Figure 8',results='hide',warning=FALSE}
#Bar plot for the question "Through what avenue do you most judge a political candidate?"
my_data %>%
  ggplot(aes(x = Gather_info)) + 
  geom_bar(color = 'black',fill = "orange") + 
  labs(title="Oulets that voters use most to judge a candidate",
       x = "Media Outlets",
       y = "Number of responses",
       caption = "Figure 8 - Source: Simulated dataset.") + 
  theme_minimal()
```

# How probabilities were calculated for simulating data for our survey 

Probability distribution for question 1 “How old are you”
Using data from the 2016 Canadian census, we calculated the population spread among different age groups over the age of 18 in Ontario. We then added a Prefer not to say option and allocated 2% of answers there to mimic a real survey.
 
Probability distribution for question 2 “How likely are you to vote in the upcoming election?”
Using estimated voter turnout by age group from Elections Canada and age distribution provided by the 2016 Canadian census, we spiked the probabilities to match the 65.63% overall voter turnout. We however assumed that at least 75 % of the population would plan to vote and that the 9.37% that didn't vote was circumstantial.The 75% was then split in a 1:1 ratio for very likely and likely. Next we then assumed that roughly 2% of people answering would choose the Don't Know/Prefer Not to answer option, and the remaining 23% was split evenly between Unlikely and Very Unlikely. 

Probability distribution for question 3“How satisfied are you with the current operation of the Ontario government?”
Through using data from the ces2015 web study, we found that almost 35% of respondents were not satisfied at all with the current operation of the government, 25% felt that they were not very satisfied, another 25% expressed fair satisfaction, 10% expressed a great deal of satisfaction and the remaining 5% were neither satisfied or dissatisfied.

Probability distribution for question 4 “What is your opinion on the Minimum Wage rate in the Province?” 
Using data from ISideWith polls, we found that 54% of Ontarians voted to raise the minimum wage and the remaining 46% voted to not raise it. We then split the remaining 46% into 23% for “just right”, 20% for “too low” and 3% for the “Don’t care/NA” option.

Probability distribution for question 5 “In your opinion, taxes for those with an income:” 
We saw through data from the ISideWith Polls that about 67% of Ontarians voted believe that the wealthy should be taxed more and 33% voted that they shouldn't. We then divided probabilities to 67% for increase rates, 20% for keep rates the same, 8% for lower rates and the remaining 5% for no opinion option.  We felt this was justified as the wealthy account for such a small percentage of the population and people voting against increasing rates most likely were voting to keep them the same. The next 2 income brackets are represented fairly evenly in Ontario at about 48% of the population each. For this reason we estimated only a small percentage of votes would go to increase rates and the majority would go to either keep rates the same or lower them. We estimated for the income bracket $40,000 to $200,000,  that 8% of voters responded in favor of increasing tax rates, 55% voted to decrease increase rates, 32% of people voted to keep the same rates as last year and 5% voted for the no opinion option. Finally for people making less than $40,000 in annual income, we estimated that 7% of people voted to increase rates, 65% of people voted to decrease rates, 24% of people voted to keep the same rates as last year and 4% of people voted for the no opinion option.

Probability distribution for question 6 “On a scale from 1 to 5, how important do you think the preservation of Ontario's environment is?” 
Through averaging the data for survey results from ISideWith polls on a number of environment related questions, we found that about 70%-80% of people voted towards the environmentally friendly option. For this reason  we split 70% of the votes between a 4/5 rating on how important safeguarding the environment is to them. The remaining 30% was split evenly among 1, 2 and 3 levels of importance.

Probability distribution for question 7 “How much money would you like to see go toward benefiting those on welfare?”
Through using data from ces2015 web study we found that 25% of Ontarians voted for less spending on welfare, 30% voted for more spending on welfare and about 40% voted for the same level of spending as the previous year. We then allocated 5% of votes to don't know/No opinion.

Probability distribution for question 8 “How much money should be spent on Healthcare facilities in Ontario?”
 Through using data from ISideWith polls, we found that about 78% of Ontarians voted to spend more on health facilities and 20% voted not to increase spending. We then averaged the 20% evenly across spending less and spending the same amount as last year and allocated 2% of votes to Don't know/No opinion option.

Probability distribution for question 9 “What do you think about the current price of hydroelectricity in Ontario?”
Through using survey data from ISideWith polls, we found that 65% of Ontarians voted to nationalize hydro and the remaining 35% of them voted to keep it privatized.However, 17% of the 35% who voted to keep it privatized said there needed to be price oversight. Hydro prices in Ontario have been a very talked about issue and with these survey results we estimated that at the very least 75% of Ontarians felt that hydro prices were too expensive. We only allocated *8% of votes to "too cheap" as these rates have increased drastically since the privatization of Hydro One back in 2015. We then assigned the remaining 17% to "fairly priced" and "No opinion" at 15% and 2% respectively.

Probability distribution for question 10 “Through what avenue do you most judge a political candidate?”
From analyzing data from a poll conducted by the CBC last year, we found that 52% of Canadians got their news information from Social media alongside online news outlets. However since this was an online survey we found that it was biased towards people that use the internet more and does not accurately represent the population correctly. We estimated that there  was a 15% bias for both online categories in this survey resulting in 37% of votes going towards social media and 25% of votes going to online news sources. The remaining 54% were split to 36% to TV , 10% to Candidate address and speeches, 5% to Newspaper articles and the remaining 3% to “other”. We felt that since people Ages 45+ take up the majority of the populous in Ontario, that 36% should be allocated towards TV as Canadian news stations like CBC are their main source for gathering political information.  
